\section{Vulnerability issues}

\begin{frame}[t]{Predictable execution}
\begin{itemize}
  \item Why doesn't software do what I expect?
    \begin{itemize}
      \item Incorrect specifications.
      \item Configuration management mistakes.
      \item \ldots
      \item Unexpected behaviour of programming language.
    \end{itemize}

  \vfill\pause
  \item What is \textmark{predictable execution}?
    \begin{itemize}
      \item Property of a program.
      \item All possible executions have results that can be predicted from examination 
            of source code.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Getting predictable software}
\begin{itemize}
  \item Software may be used:
    \begin{itemize}
      \item On unanticipated platforms.
      \item On unanticipated ways.
      \item On unanticipated contexts.
      \item By unanticipated users.
    \end{itemize}

  \vfill
  \item Additionally:
    \begin{itemize}
      \item We are in a connected world.
      \item Cyberattacks!
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Software vulnerabilities}
\begin{itemize}
  \item \textmark{Software vulnerability}: \textbad{Unwanted} characteristic of software
        that may allow software to execute in ways that are unexpected.

    \begin{itemize}
      \item Programmers introduce vulnerabilities by using language features that are
            unpredictable.
    \end{itemize}

  \vfill\pause
  \item \textmark{Language vulnerability}: Property of a programming language that can
        contribute to application vulnerabilities.
    \begin{itemize}
      \item Security weakness.
      \item Safety hazard.
      \item Software defect.
    \end{itemize}

  \vfill\pause
  \item \textgood{Example}:
    \begin{itemize}
      \item \textbad{Language vulnerability}: String copy does not check length.
      \item \textbad{Application vulnerability}: Stack attack through buffer overrun.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Sources of unpredictability}
\begin{itemize}
  \item Incomplete or evolving specifications.
  \item Undefined behaviour.
  \item Unspecified behaviour.
  \item Implementation defined behaviour.
  \item Difficult features.
  \item Inadequate language support.

  \vfill\pause
  \item Additionally:
    \begin{itemize}
      \item Porting to other platforms.
      \item Compilers might also have bugs.
      \item Use of different compiler switches.
    \end{itemize}
\end{itemize}
\end{frame}

