\subsection{P.1: Express ideas directly in code}

\begin{frame}[t,fragile]{Express ideas in code}
\begin{itemize}
  \item Why?
    \begin{itemize}
      \item Comments (or design documents) are not always in synch with code.
      \item Code has defined semantics.
    \end{itemize}

  \mode<presentation>{\vfill\pause}
  \item Implications:
    \begin{itemize}
      \item This philosophical principle has many ramifications.
      \item Some of them are difficult to enforce.
    \end{itemize}
\end{itemize}

\mode<presentation>{\vfill\pause}
\begin{columns}

\column{.5\textwidth}
\begin{block}{Bad}
\begin{lstlisting}
class date {
public:
  int month();
  //...
};
\end{lstlisting}
\end{block}

\pause
\column{.5\textwidth}
\begin{block}{Good}
\begin{lstlisting}[escapechar=@]
class date {
public:
  @\color{red}month\_id@ month()@\color{red}const@;
  //...
};
\end{lstlisting}
\end{block}

\end{columns}

\end{frame}

\begin{frame}[t,fragile]{Use code to express intent}
\begin{itemize}
  \item The standard library helps to better express intent.

\pause
\begin{block}{Bad}
\begin{lstlisting}
double f(const std::vector<double> & v) {
  double s = 0.0;
  for (std::size_t i=0; i<v.size(); ++i) {
    x += v[i];
  }
  return s / v.size();
}
\end{lstlisting}
\end{block}

\pause
\begin{block}{Good}
\begin{lstlisting}
double average(const std::vector<double> & v) {
  double s = std::reduce(v.begin(), v.end());
  return s / v.size();
}
\end{lstlisting}
\end{block}

\end{itemize}
\end{frame}

\begin{frame}[t]{Enforcement}
\begin{itemize}
  \item Very hard to enforce in general.

  \mode<presentation>{\vfill\pause}
  \item Some particular enforcements:
    \begin{itemize}
      \item Use const consistently.
        \begin{itemize}
          \item Flag non const function with const behaviour. 
          \item Flag non const reference pointer arguments that are not modified.
        \end{itemize}

      \pause
      \item Flag uses of casts.
        \begin{itemize}
          \item Casts are a way to bypass the type system.
        \end{itemize}
      \pause
      \item Try to detect code that mimics standard library.
        \begin{itemize}
          \item Many loops better expressed by standard algorithms.
          \item Very difficult to detect.
        \end{itemize}
    \end{itemize}
\end{itemize}
\end{frame}
